Bitmap Indexing for Fast Analysis of Large Astrophysical Datasets

### 2016-08-31 ms/ms.tex
Minor changes and commenting of todos

@@

Bitmap indexing is particularly useful in astronomy and astrophysics. Output from N-body simulations is often split between multiple files to take advantage of parallel I/O and the domain decomposition generally leads to localized partitioning between files \citep{Springel2001,Springel2005b,Hopkins2015}. \todo{applications outside astronomy}

@@

%---------------------------------------------------------------------------------
% CODE
\section{Code}\label{S:code}
These procedures have been implemented as part of the {\tt yt} python package
\citep{Turk20d11a} in order to facilitate the analysis of large astrophysical
N-body simulations; currently undergoing review for inclusion in a future version of {\tt yt} (3.4 or later), our implementation is available at \url{https://bitbucket.org/langmm/yt-bitmap}. The open source EWAHBoolArray C++ package is used for implementing EWAH bitmaps \citep{Lemire2010,Kaser2016} and exposed to Python using Cython \citep{Behnel2011}. All of the code used to run and plot the tests presented here is available for download at \todo{website}.

%---------------------------------------------------------------------------------
% ACKNOWLEDGMENTS
\acknowledgments
This publication is supported in part by the Gordon and Betty Moore
Foundation’s Data-Driven Discovery Initiative through Grant GBMF4561 to Matthew
Turk.  This material is based upon work supported by the National Science
Foundation under Grant No.~ACI-1535651.  The authors would like to thank Daniel
Lemire for his open source EWAH implementation.  {\tt yt} is developed by a
large number of independent research from numerous institutions around the
world.  Their committment to open science has helped make this work possible.

>>>>

Overall, this technique offers a considerable improvement in performance over other methods that require reading, evaluating and discarding all of the particles.

@@

Bitmap indexing is particularly useful in astronomy and astrophysics. Output from N-body simulations is often split between multiple files to take advantage of parallel I/O and the domain decomposition generally leads to localized partitioning between files \citep{Springel2001,Springel2005b,Hopkins2015}. %\todo{applications outside astronomy}

@@

%---------------------------------------------------------------------------------
% CODE
\section{Code}\label{S:code}
These procedures have been implemented as part of the {\tt yt} python package
\citep{Turk20d11a} in order to facilitate the analysis of large astrophysical
N-body simulations; currently undergoing review for inclusion in a future version of {\tt yt} (3.4 or later), our implementation is available at \url{https://bitbucket.org/langmm/yt-bitmap}. The open source EWAHBoolArray C++ package is used for implementing EWAH bitmaps \citep{Lemire2010,Kaser2016} and exposed to Python using Cython \citep{Behnel2011}.

%---------------------------------------------------------------------------------
% ACKNOWLEDGMENTS
\acknowledgments
This publication is supported in part by the Gordon and Betty Moore
Foundation’s Data-Driven Discovery Initiative through Grant GBMF4561 to Matthew
Turk.  This material is based upon work supported by the National Science
Foundation under Grant No.~ACI-1535651.  The authors would like to thank Daniel
Lemire for his open source EWAH implementation.  {\tt yt} is developed by a
large number of independent researchers from numerous institutions around the
world.  Their commitment to open science has helped make this work possible.
